\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Dilshad Ansari} \\ \vspace{1pt}
    \small +91 9319475235 $|$ \href{mailto:x@x.com}{\underline{rdilshad3559@gmail.com}} $|$ 
    \href{https://linkedin.com/in/dilshad-ansari-dev}{\underline{linkedin.com/in/dilshad-ansari-dev}} $|$
    \href{https://github.com/...}{\underline{github.com/lytcode404}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Netaji Subhash University of Technology}{Delhi}
      {Bachelor's Degree in Electronics and Communication Engineering – (CGPA –7.6)}
      {Nov 2022 -- Present}
       {  \newline in Artificial Intelligence and Machine Learning }
    \resumeSubheading
      {Rajkiya Pratibha Vikas Vidyalaya, Dwarka Sec 5}{Delhi}
      {Higher Secondary Education - (Class 12 - 91.6\%)}{May 2020 -- May 2021}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Javascript, Django, Flask, Cython, JavaScript, Go, Shell Scripting (Bash), C/C++, SQL (Postgres), HTML/CSS} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Express Js, WordPress, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, AWS, VS Code, Jupyter Notebook, Google Colab} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib , Keras, Tensorflow, Sci-kit Learn}
    }}
 \end{itemize}

 
%-----------EXPERIENCE------------------------------------------------------------------------------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading  
    {Full Stack Developer}{Oct 2024 - Dec 2024}  
    {E-commerce Website (adiprabha.com)}{Delhi}  
    \resumeItemListStart  
      \resumeItem{Developed and deployed a fully responsive e-commerce platform using ReachJs, Nextjs, and Tailwind CSS, ensuring fast load times and a seamless user experience across 98\% of devices.}  
      \resumeItem{Engineered a secure backend with Firestore DB and Nodejs, handling more than 1,000 product records, while integrating Google Authentication for smooth user sign-in processes.}  
      \resumeItem{Created an intuitive Admin panel, enabling administrators to upload, edit, and delete products, enhancing management efficiency by 40\% and providing visually engaging designs with Tailwind CSS.}  
    \resumeItemListEnd


  \resumeSubheading  
    {Full Stack Next.js Developer}{Feb 2024 - May 2024}  
    {ARW Tours and Travels (arwtoursandtravelsgoa.com)}{Delhi}  
    \resumeItemListStart  
      \resumeItem{Designed a travel booking platform with trip planning tools, destination guides, sightseeing suggestions, and hotel reservations, increasing user engagement by 25\% and supporting over 10,000 bookings.}  
      \resumeItem{Optimized backend and APIs, reducing server costs and improving website performance by 40\% through code refactoring, improved caching, and streamlined database queries.}  
      \resumeItem{Surpassed industry benchmarks against Tripplanner.in and Templemitra.com, achieving a 20\% growth in the user base and strengthening market presence through targeted outreach.}  
    \resumeItemListEnd  

  \resumeSubheading  
    {Full Stack MERN Developer}{Aug 2023 -- Jan 2024}  
    {Phoenix Ventures (phoenixventures.me)}{Delhi}  
    \resumeItemListStart  
      \resumeItem{Engineered an advanced admin panel for business enlistment on Paronama, reducing backend integration time by 40\% and increasing user-business interactions by 25\%.}  
      \resumeItem{Developed a scalable Node.js, Express.Js backend, improving response times by 30\% through optimized Firebase NoSQL queries and efficient API design.}  
      \resumeItem{Enhanced website security by integrating advanced authentication mechanisms, improving access control by 40\% and ensuring robust data protection.}  
    \resumeItemListEnd  

  % \resumeSubheading  
  %   {Full Stack MERN Developer}{Sep 2023 -- Dec 2023}  
  %   {Carskarkhana}{Delhi}  
  %   \resumeItemListStart  
  %     \resumeItem{Designed a REST API using Express.js, Node.js, and Firebase, reducing server response time by 20\%.}  
  %     \resumeItem{Architected three scalable backends and APIs, cutting database storage costs by 30\%.}  
  %     \resumeItem{Implemented a multi-layered authentication system, reducing unauthorized access attempts by 30\%.}  
  %     \resumeItem{Created clean, responsive user interfaces, leading to a 40\% increase in user engagement.}  
  %   \resumeItemListEnd  

  \resumeSubHeadingListEnd  

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

  \resumeProjectHeading  
    {\textbf{Shop Smart Analyser} $|$ \emph{React.js, Node.js, Python, Chrome Inbuilt APIs}}{Apr 2024}  
    \resumeItemListStart  
      \resumeItem{Achieved 1st place, outperforming thousands of competing teams, and secured a 12 lakh prize pool at AMDOCS MOKSHA INNOVISION.}  
      \resumeItem{Implemented Chrome APIs to analyze over 100 Flipkart product listings with reduced server load and an average response time under 200 ms.}  
    \resumeItemListEnd  

  \resumeProjectHeading  
    {\textbf{Crypto Bubbles} $|$ \emph{Next.js, Node.js, TailwindCSS, Flask, Python, Vercel}}{May 2018 -- May 2020}  
    \resumeItemListStart  
      \resumeItem{Created a visually intuitive web application for displaying cryptocurrency data through dynamically floating cloudy bubbles and over 10 parameters for in-depth cryptocurrency analysis.}  
      \resumeItem{Ranked in the top 10 at Adobe DevCraft hosted at DTU for innovative web development.}  
    \resumeItemListEnd  

  \resumeSubHeadingListEnd




%-------------------------------------------
\end{document}